Sparse Function-space Representation \\ of Neural Networks

### 2023-05-12 paper/main.tex
started doing rl stuff

\textbf{Reinforcement learning}

>>>>

\textbf{Model-based reinforcement learning}
We now detail how our method can be used in model-based RL.
Folling the Markov decision process formulation \cite{bellmanDynamic1956}, we
denote states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \), actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and
transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to  i.i.d. transition noise \(\noise_{t}\).
The goal of RL is to find the policy \(\pi \in \Pi \) that maximises the sum of rewards
in expecation over the transition noise,
\begin{align} \label{eq-model-free-objective}
\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right]
\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
\end{align}
where $\gamma \in [0, 1]$ is a discount factor to account for the infinte sum.

In model-based RL, the state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\) is first used to
learn a dynamic model \(f_{\mathbf{w}})\) using supervised learning.
\cref{alg-mbrl} shows the typical model-based RL loop.

\begin{subequations}
\begin{align} \label{eq-fast-update-mpc}
  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1})
\end{align}
\end{subequations}
\begin{subequations}
\begin{align} \label{eq-fast-update-mpc-old}
  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
\end{align}
\end{subequations}

In model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
\cref{alg-mbrl} shows the typical model-based RL loop.
Importantly, the dynamics are usually only updated after an episode $i$.

\textbf{Posterior sampling}
Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,

\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
\begin{align} \label{eq-posterior-sampling}
\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
\end{align}
